Bayesian regression facilitates quantitative modelling of cell metabolism

### 2023-10-31 paper/main.qmd
multiomics inaccuracies

A kinetic model of cellular metabolism aims to express what is known
about a cellular process in the form of an *in silico* representation
of the underlying network of chemical reactions. Kinetic models can be
used to improve production of target molecules, determine regulatory
networks [@christodoulou_reserve_2018] and identify potential drug targets
[@deberardinis_fundamentals_2016;@Liberti2017]. However, the use of kinetic
models in practice is hindered by their dependence on noisy and uncertain
information sources. Quantitative in vivo measurements of chemical abundances,
and in vitro measurements relating to kinetic parameters, both contain vital
information but are notoriously inaccurate (REFERENCES). Practically useful
kinetic modelling therefore requires a principled statistical approach that
encompasses multiple possible model parameterisations.

>>>>

A kinetic model of cellular metabolism aims to express what is known
about a cellular process in the form of an *in silico* representation
of the underlying network of chemical reactions. Kinetic models can be
used to improve production of target molecules, determine regulatory
networks [@christodoulou_reserve_2018] and identify potential drug targets
[@deberardinis_fundamentals_2016;@Liberti2017]. However, the use of kinetic
models in practice is hindered by their dependence on noisy and uncertain
information sources. Quantitative in vivo measurements of chemical abundances,
and in vitro measurements relating to kinetic parameters, both contain vital
information but are notoriously inaccurate [siskos2017; tabb2010]. Practically useful
kinetic modelling therefore requires a principled statistical approach that
encompasses multiple possible model parameterisations.
